### 2021-10-31 publication/experiments.tex
Reduce to two figures

@@

The goal here is to 
determine whether the authors' political affiliations are a good predictor 
of the overall network structure. We choose to partition the network into $B=3$ communities as we only have this many distinct values for political affiliation (conservative, liberal or neutral).
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.452\linewidth}
		\centering
		\vskip 0pt
		\includegraphics[width=\linewidth]{polbooks-null-1}
		\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
		\label{fig:polbooks-null}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\vskip 0pt
		\includegraphics[width=\linewidth]{polbooks-accuracy-1}
		\caption{Per-block accuracy $\eta(j)$.}
		\label{fig:polbooks-accuracy}
	\end{subfigure}
	\caption{Political books dataset.}
	\label{fig:polbooks}
\end{figure}

From Figure~\ref{fig:polbooks-null} we see that all 3 blocks have a distinct political affiliation as their largest positive component. 
This strongly indicates that political affiliation is indeed the axis 
which best predicts the 3-way natural partition of the graph into blocks. 
Furthermore, in Table~\ref{tab:results} we see that the training and test losses 
are very similar and both are low in magnitude. This provides further evidence 
to the claim that political affiliation is a very appropriate explanatory 
variable for the overall network structure.

However, from Figure~\ref{fig:polbooks-accuracy} we see that block 1 has low accuracy. 
This suggests that detected block 1 is not solely composed of ``neutral" books but also 
contains some ``liberal" and ``conservative" authors. Indeed, by examining 
Figure~\ref{fig:polbooks-graph} we see that block 1 is effectively a buffer between 
blocks 2 and 3; there are very few edges between blocks 2 and 3. It is therefore not 
surprising that some books from either side leak into block 1.
Perhaps, the three distinct categories (``conservative", ``liberal", ``neutral") are 
too coarse a measure of political affiliation; it may be the case that the nominally 
``conservative" books found in block 1 are in fact more centre-right. 
In the absence of more granular labels, we cannot test this hypothesis. 
Nevertheless, political affiliation encoded as 3 distinct labels 
remains a fantastic predictor of network structure.

@@

We choose the number of communities $B=10$, in line with the total number of 
school classes. As before, we sample the block-generator parameters $\theta$ and 
employ the dimensionality reduction technique 
of Section~\ref{sec:dim-reduction},
with standard deviation multiplier $k=1$ to pick out the top $D'=10$ features. 
We then plot the weights for the resulting features $d \in \Dcal'$ 
in Figure~\ref{fig:school-null}. It is rather obvious
that only the pupils' class memberships (1A-5B) have remained
significant;
gender and teacher/student status have been discarded,
meaning that these are not good predictors of overall macro-structure.
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{0.8\linewidth}{\includegraphics[width=\linewidth]{school-null-1}}
		\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
		\label{fig:school-null}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{0.8\linewidth}{\includegraphics[width=\linewidth]{school-accuracy-1}}
		\caption{Per-block accuracy $\eta(j)$.}
		\label{fig:school-accuracy}
	\end{subfigure}
	\caption{Primary school dynamic contacts dataset.}
	\label{fig:school}
\end{figure}

@@

We choose $B=10$ and $D'=10$ for this experiment. The selected features 
(Figure~\ref{fig:fb-null}) are those that best explain the high-level 
community structure. The majority of them are education related. 
Nevertheless, for $D'=10$ we only have good explanations for the makeup 
of some of the detected blocks; several blocks in 
Figure~\ref{fig:fb-null} do not have high-magnitude components for $D'=10$. This is further emphasised by the disparate accuracies in Figure~\ref{fig:fb-accuracy}. Nevertheless, observe that the accuracy is only high for blocks that contain high magnitude weights. The only exception to this rule is block 9 which nonetheless may have high magnitude weights just below the cut-off $c^*$.
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-null-1}}
		\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
		\label{fig:fb-null}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\linewidth}
		\centering
		\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-accuracy-1}}
		\caption{Per-block accuracy $\eta(j)$.}
		\label{fig:fb-accuracy}
	\end{subfigure}
	\caption{Facebook egonet dataset.}
	\label{fig:fb}
\end{figure}

>>>>

\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{polbooks-null-1}}
			\caption{Political Books.}
			\label{fig:polbooks-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{school-null-1}}
			\caption{Primary School.}
			\label{fig:school-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-null-1}}
			\caption{Facebook Egonet.}
			\label{fig:fb-null}
		\end{subfigure}
	\caption{$\theta$-samples. Dotted line is $\pm c^*$.}
\end{figure}
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{polbooks-accuracy-2}}
			\caption{Political Books.}
			\label{fig:polbooks-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{school-accuracy-1}}
			\caption{Primary School.}
			\label{fig:school-null}
		\end{subfigure}
	\begin{subfigure}[t]{0.32\linewidth}
			\centering
			\imagebox{0.9\linewidth}{\includegraphics[width=\linewidth]{fb-accuracy-1}}
			\caption{Facebook Egonet.}
			\label{fig:fb-null}
		\end{subfigure}
	\caption{Per-block accuracy $\eta(j)$.}
\end{figure}

@@

The goal here is to 
determine whether the authors' political affiliations are a good predictor 
of the overall network structure. We choose to partition the network into $B=3$ communities as we only have this many distinct values for political affiliation (conservative, liberal or neutral).

From Figure~\ref{fig:polbooks-null} we see that all 3 blocks have a distinct political affiliation as their largest positive component.  
Furthermore, in Table~\ref{tab:results} we see that the training and test losses 
are very similar and both are low in magnitude. This is strong evidence 
that political affiliation is a very appropriate explanatory 
variable for the overall network structure.

However, from Figure~\ref{fig:polbooks-accuracy} we see that block 1 has low accuracy. 
This suggests that detected block 1 is not solely composed of ``neutral" books but also 
contains some ``liberal" and ``conservative" authors. Indeed, by examining 
Figure~\ref{fig:polbooks-graph} we see that block 1 is effectively a buffer between 
blocks 2 and 3; there are very few edges between blocks 2 and 3. It is therefore not 
surprising that some books from either side leak into block 1.
The three distinct categories may be 
too coarse a measure of political affiliation; perhaps the nominally 
``conservative" books found in block 1 are closer to the centre. 
In the absence of more granular labels, we cannot test this hypothesis. 
Nevertheless, political affiliation encoded as 3 distinct labels 
remains a fantastic predictor of network structure.

@@

We choose the number of communities $B=10$, in line with the total number of 
school classes. We 
employ the dimensionality reduction technique to pick out the top $D'=10$ features. 
We then plot the weights for the resulting features $d \in \Dcal'$ 
in Figure~\ref{fig:school-null}. It is rather obvious
that only the pupils' class memberships (1A-5B) have remained
significant;
gender and teacher/student status have been discarded,
meaning that these are not good predictors of overall macro-structure.

@@

We choose $B=10$ and $D'=10$ for this experiment. The selected features 
(Figure~\ref{fig:fb-null}) are those that best explain the high-level 
community structure. The majority of them are education related. 
Nevertheless, for $D'=10$ we only have good explanations for the makeup 
of some of the detected blocks; several blocks in 
Figure~\ref{fig:fb-null} do not have high-magnitude components for $D'=10$. This is further emphasised by the disparate accuracies in Figure~\ref{fig:fb-accuracy}. Nevertheless, observe that the accuracy is only high for blocks that contain high magnitude weights. The only exception to this rule is block 9 which nonetheless may have high magnitude weights just below the cut-off $c^*$.

### 2021-10-31 publication/inference.tex
Reduce to two figures

		% arrows
		\draw[->] (b0) to node[above] {$\sim q_b(b^{(t)}, b' | A)$} (b1);
		\draw[->] (b1) to node[above] {$\alpha_b (b, b' | A)$} (b2);
		\draw[->] (b0) [out=30, in=150] to node[above] {$1-\alpha_b$} (b2);

		\draw[->] (t0) to node[above] {$\sim q_\theta(\theta^{(t)}, \theta' | X, b^{(t)})$} (t1);
		\draw[->] (t1) to node[above] {$\alpha_\theta (\theta, \theta' | X, b^{(t)})$} (t2);
		\draw[->] (t0) [out=-30, in=-150] to node[below] {$1-\alpha_\theta$} (t2);

@@

We adopt the Markov chain Monte-Carlo procedure of
\cite{Peixoto-MCMC},
which relies on writing the posterior in the following form:
%
\begin{equation}
	p(b | A, X) \propto p(A | b, X) \cdot p(b | X) = \pi_b(b).
\end{equation}
%
Now $\pi_b(\cdot)$ is the un-normalised target density,
which can be expressed as:
%  we wish to sample from for the $b$-chain. In other words, we 
% wish to construct a Markov chain that has $\pi_b(\cdot)$ 
% as its invariant distribution. We can break $\pi_b$ down as follows:
%
\begin{equation}
	\pi_b(b) = p(b|X) \sum_{\psi} \nolimits p(A , \psi | b, X) \\
	= p(b|X) p(A, \psi^* | b, X) \\
	= p(A | b, \psi^*) \cdot p(\psi^* | b) \cdot p(b | X).
\end{equation}
%
Since we are using the microcanonical SBM formulation, there is only one 
value of $\psi$ that is compatible with the given $(A, b)$ pair;
recall the constraints in~(\ref{eqn:sbm-constraints}). 
We denote this value $\psi^* = \{\psi_k^*, \psi_e^*\}$. Therefore, 
the summation over all $\psi$ reduces to just the single $\psi^*$ term.
% ; this is the power of the microcanonical formulation. 
We also define the microcanonical entropy of the configuration as,
%
\begin{equation}
	S(b) = - \log \pi_b(b) = - \Big( \log p(A | b, \psi^*) + \log p(\psi^*, b | X) \Big).
	\label{eqn:dl-form}
\end{equation}
%
This entropy can be thought of as the optimal
``description length'' of the graph; if we 
constructed an optimal code for the SBM ensemble,
this would be the minimum amount of information 
required to store the graph and its parameters. 
The exact form of the proposal $q_b$ is explored thoroughly in
\cite{Peixoto-MCMC} and not repeated here. There is a widely used 
library for Python made available under LGPL 
called \verb*|graph-tool| \cite{peixoto_graph-tool_2014}, 
which implements this algorithm. The only modification we make is in 
the block membership prior $p(b)$ that we replace with $p(b|X)=B^{-N}$, 
which cancels out in the MH accept-reject step as it is independent of $b$.

@@

See Appendix \ref{appdx:form-U} for the derivation. The function $U(\theta)$ is a typical objective function for neural network training. The first term is introduced by the likelihood; we collect it into $N \cdot \Lcal(\theta)$, which is the cross-entropy between the graph-predicted and feature-predicted block memberships summed over all vertices. 
The second, introduced by the prior, brings a form of regularisation, guarding against over-fitting. Unlike in many applications where the goal 
is to find the minimiser of $U(\theta)$, our goal is to draw samples from the posterior $\pi_\theta(\cdot) \propto \exp(-U(\cdot))$. We can use $\nabla U$ as a useful heuristic to bias our proposal towards regions of higher target density. We therefore adopt the Metropolis-adjusted Langevin algorithm (MALA) \cite{mala-tweedie}. Given the current sample $\theta$, we generate 
a new sample $\theta'$ as,
%
\begin{equation*}
	\theta' = \theta - h \nabla U(\theta) + \sqrt{2h} \cdot \xi,
\end{equation*}
%
where $\xi \sim \Gaussian(0, I)$ and $h$ is a step-size parameter 
which may vary with the sample index.
This leads to the proposal distribution,
\begin{equation*}
	q_\theta(\theta, \theta') \sim \Gaussian \left( \theta' ; \theta - h \nabla U(\theta), 2h I \right).
\end{equation*}
%
Without the injected noise term, MALA is equivalent to gradient descent. We require the noise term $\xi$ to fully explore the parameter space. 
The term $\nabla U$ has an easy to compute analytic form (derived in Appendix \ref{appdx:gradu}). By noting that $\theta = \{w_k\}_{k=1}^{B}$, we write the derivative with respect to each $w_k$ as,
%
\begin{equation}
	\frac{\partial U}{\partial w_k} = - \left( \sum_{i \in [N]} \Big\{ x_i (y_{ik} - a_{ik}) \Big\} - \frac{w_k}{\sigma_\theta^2} \right).
	\label{eqn:U-derivative}
\end{equation}
%
After a proposed move is generated from $q_\theta$,
it is either accepted or rejected in the standard
Metropolis-Hastings accept/reject step.

@@

Up to this point, each $\theta^{(t)}$ update uses its corresponding $b^{(t)}$ sample. This means that the evaluation of $U(\theta)$ and $\nabla U(\theta)$ has high variance. This may lead to longer burn-in for the resulting Markov chain. The only link between $b^{(t)}$ and $\theta^{(t)}$ is in the evaluation of $U(\theta)$ and $\nabla U(\theta)$ which depends only on the matrix $y^{(t)}$ with entries $y_{ij}^{(t)} \coloneqq \one\{b_i^{(t)} = j\}$. We would rather deal with the expectation of each $y_{ij}^{(t)}$:
%
\begin{equation}
	\Expect \left[ y_{ij}^{(t)} \right] = \Expect_{b^{(t)}} \left[ \one(b_{i}^{(t)} = j) \right]
	= p(b_i = j | A, X).
\end{equation}
%
We can obtain an unbiased estimate for this quantity using 
the thinned $b$-samples after burn-in.
Let $\Tcal_b$  denote the retained set of indices 
for the $b$-samples and $\Tcal_\theta$ similarly for the $\theta$-chain. 
The unbiased estimate for $y_{ij}^{(t)}$ using the 
restricted sample set $\Tcal_b$ is denoted $\hat{y}_{ij}$:
%
\begin{equation}
	\hat{y}_{ij} \coloneqq \frac{1}{|\Tcal_b|} \sum_{t \in \Tcal_b} y_{ij}^{(t)} = \frac{1}{|\Tcal_b|} \sum_{t \in \Tcal_b} \one\{b_i^{(t)} = j\}.
	\label{eqn:y-hat}
\end{equation}
%
The same matrix $\hat{y}$ is used in the update step
for each $\theta^{(t)}$.
This way, it is not necessary to run the $b$ and $\theta$ Markov chains 
concurrently. Instead, we run the $b$-chain to completion and use it 
to generate $\hat{y}$. This affords us the flexibility to vary the 
lengths of the $b$ and $\theta$-chains. Furthermore, the changeover 
from $y^{(t)}$ to $\hat{y}$ reduces the burn-in time for 
the $\theta$-chain by reducing the variance in the evaluation 
of $U$ and $\nabla U$.

@@

Once the samples $\left\{ \theta^{(t)} \right\} \sim p(\theta | A, X)$
have been obtained, we can compute the empirical mean and standard deviation of each component of $\theta$. Switching back to matrix notation, we define $\theta = W$, such that $W_{ij}$ is the weight component for block $i$ and feature $j$. We can then define:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} W_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma}_{ij}^2 \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2.
\end{equation}
%
A simple heuristic to discard the least important features requires specifying a cutoff $c > 0$ and a multiplier $k > 0$. We define the function $\Fcal_i(j)$ 
as in~(\ref{eqn:fij}) and only keep features with indices $d \in \Dcal'$, where $\Dcal'$ is given in~(\ref{eqn:kept-feature-set}).
%
\begin{align}
	\Fcal_i(j) &\coloneqq (\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c),
	\label{eqn:fij} \\
	\Dcal' &\coloneqq \left\{ j \in [D] : \exists i \in [B] \textrm{ s.t. }  \Fcal_i(j) = \emptyset \right\}
	\label{eqn:kept-feature-set}
\end{align}
%
Intuitively, this means discarding any feature $j$ for which 
$(\hat{\mu}_{ij} - k\hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij})$ overlaps with
$(-c, c)$ for all block indices $i$. If we were to use the Laplace approximation for the posterior $p(W_{ij} | A, X) \approx \Gaussian(W_{ij}; \hat{\mu}_{ij}, \hat{\sigma}_{ij}^2)$, then this is analogous to a hypothesis test on the value of $W_{ij}$ as in~(\ref{eqn:hyp-test-discard});
then $\Dcal'$ comprises all features $j$ for which $H_1$ is accepted at least once for some $i \in [B]$.
%
\begin{equation}
	H_0: |W_{ij}| \leq c \qquad
	H_1: |W_{ij}| > c
	\label{eqn:hyp-test-discard}
\end{equation}
%
The multiplier $k$ in~(\ref{eqn:fij}) determines the degree of significance of the result. However, as the Laplace approximation is not exact, we only treat this dimensionality reduction method as a useful heuristic and not an exact method.

Conversely, we could fix $k=k_0$ and the dimension of our reduced feature set $|\Dcal'|=D'$. We would then like to find the largest value of $c$ such that $|\Dcal'|=D'$ given $k=k_0$. This is summarised in equation \ref{eqn:c-star}.
%
\begin{equation}
	c^* = \argmax \{c>0\; : \;|\Dcal'| = D', k=k_0\}.
	\label{eqn:c-star}
\end{equation}
%
This approach has the advantage that it fixes the number of reduced dimensions.

>>>>

		% arrows
		\draw[->] (b0) to node[above] {$\sim q_b ( b^{(t)}, b' | A )$} (b1);
		\draw[->] (b1) to node[above] {$\alpha_b (b, b' | A )$} (b2);
		\draw[->] (b0) [out=25, in=155] to node[above] {$1-\alpha_b$} (b2);

		\draw[->] (t0) to node[above] {$\sim q_\theta(\theta^{(t)}, \theta' | X, b^{(t)})$} (t1);
		\draw[->] (t1) to node[above] {$\alpha_\theta (\theta, \theta' | X, b^{(t)})$} (t2);
		\draw[->] (t0) [out=-25, in=-155] to node[below] {$1-\alpha_\theta$} (t2);

@@

We adopt the Markov chain Monte-Carlo procedure of
\cite{Peixoto-MCMC},
which relies on writing the posterior in the following form:
%
\begin{equation}
	p(b | A, X) \propto p(A | b, X) \cdot p(b | X) = \pi_b(b).
\end{equation}
%
Now $\pi_b(\cdot)$ is the un-normalised target density.
Since we are using the microcanonical SBM formulation, there is only one 
value of $\psi$ that is compatible with the given $(A, b)$ pair;
recall the constraints in~(\ref{eqn:sbm-constraints}).
We denote this value $\psi^* = \{\psi_k^*, \psi_e^*\}$. Therefore, 
the summation over all $\psi$ needed to evaluate $p(A | b, X)$ reduces to just the single $\psi^*$ term:
$p(A | b, X) = \sum_{\psi} \nolimits p(A , \psi | b, X) = p(A, \psi^* | b, X)$.
We also define the microcanonical entropy of the configuration as,
%
\begin{equation}
	S(b) \coloneqq - \log \pi_b(b) = - \Big( \log p(A | b, \psi^*) + \log p(\psi^*, b | X) \Big).
	\label{eqn:dl-form}
\end{equation}
%
This entropy can be thought of as the optimal
``description length'' of the graph. 
The exact form of the proposal $q_b$ is explored thoroughly in
\cite{Peixoto-MCMC} and not repeated here. The \verb*|graph-tool| \cite{peixoto_graph-tool_2014}
library for Python available under LGPL implements this algorithm.
The only modification we make is in 
the block membership prior $p(b)$ that we replace with $p(b|X)=B^{-N}$, 
which cancels out in the MH accept-reject step as it is independent of $b$.

@@

See Appendix \ref{appdx:form-U} for the derivation. The function $U(\theta)$ is a typical objective function for neural network training. The first term is introduced by the likelihood; we collect it into $N \cdot \Lcal(\theta)$, which is the cross-entropy between the graph-predicted and feature-predicted block memberships summed over all vertices. 
The second, introduced by the prior, brings a form of regularisation, guarding against over-fitting. Unlike in many applications where the goal 
is to find the minimiser of $U(\theta)$, our goal is to draw samples from the posterior $\pi_\theta(\cdot) \propto \exp(-U(\cdot))$. We can use $\nabla U$ as a useful heuristic to bias our proposal towards regions of higher target density. We therefore adopt the Metropolis-adjusted Langevin algorithm (MALA) \cite{mala-tweedie}. Given the current sample $\theta$, we generate 
a new sample $\theta'$ as,
%
\begin{equation*}
	\theta' = \theta - h \nabla U(\theta) + \sqrt{2h} \cdot \xi,
\end{equation*}
%
where $\xi \sim \Gaussian(0, I)$ and $h$ is a step-size parameter 
which may vary with the sample index.
This leads to the proposal distribution,
$q_\theta(\theta, \theta') \sim \Gaussian \left( \theta' ; \theta - h \nabla U(\theta), 2h I \right).$
Without the injected noise term $\xi$, MALA is equivalent to gradient descent. We require $\xi$ to fully explore the parameter space. 
The term $\nabla U$ has an easy to compute analytic form (derived in Appendix \ref{appdx:gradu}).

@@

So far, each $\theta^{(t)}$ update has used its corresponding $b^{(t)}$ sample. This means the evaluation of $U(\theta)$ and $\nabla U(\theta)$ has high variance, leading to longer burn-in. The only link between $b^{(t)}$ and $\theta^{(t)}$ is in the evaluation of $U(\theta)$ and $\nabla U(\theta)$ which depends only on the matrix $y^{(t)}$ with entries $y_{ij}^{(t)} \coloneqq \one\{b_i^{(t)} = j\}$. We would rather deal with the expectation of each $y_{ij}^{(t)}$:
%
\begin{equation}
	\Expect \left[ y_{ij}^{(t)} \right] = \Expect_{b^{(t)}} \left[ \one \left( b_{i}^{(t)} = j \right) \right]
	= p(b_i = j | A, X).
\end{equation}
%
We can obtain an unbiased estimate for this quantity using 
the thinned $b$-samples after burn-in.
Let $\Tcal_b$  denote the retained set of indices 
for the $b$-samples and $\Tcal_\theta$ similarly for the $\theta$-chain. 
The unbiased estimate for $y_{ij}^{(t)}$ using the 
restricted sample set $\Tcal_b$ is denoted $\hat{y}_{ij}$:
%
\begin{equation}
	\hat{y}_{ij} \coloneqq \frac{1}{|\Tcal_b|} \sum_{t \in \Tcal_b} y_{ij}^{(t)} = \frac{1}{|\Tcal_b|} \sum_{t \in \Tcal_b} \one\{b_i^{(t)} = j\}.
	\label{eqn:y-hat}
\end{equation}
%
The same matrix $\hat{y}$ is used in the update step
for each $\theta^{(t)}$.
This way, it is not necessary to run the $b$ and $\theta$ Markov chains 
concurrently. Instead, we run the $b$-chain to completion and use it 
to generate $\hat{y}$ also allowing us to vary the lengths of each. This change shortens the burn-in of the $\theta$-chain by reducing the variance of our proposal distribution.

@@

Once the samples $\left\{ \theta^{(t)} \right\} \sim p(\theta | A, X)$
have been obtained, we can compute the empirical mean and standard deviation of each component of $\theta$. Switching back to matrix notation, we define $\theta = W$, such that $W_{ij}$ is the weight component for block $i$ and feature $j$. We can then define:
%
\begin{equation}
	\hat{\mu}_{ij} \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} W_{ij}^{(t)} \qquad \textrm{and} \qquad
	\hat{\sigma}_{ij}^2 \coloneqq \frac{1}{|\Tcal_\theta|} \sum_{t \in \Tcal_\theta} \left( W_{ij}^{(t)} - \hat{\mu}_{ij} \right)^2.
\end{equation}
%
A simple heuristic to discard the least important features requires specifying a cutoff $c > 0$ and a multiplier $k > 0$. We define the function $\Fcal_i(j)$ 
as in~(\ref{eqn:fij}) and only keep features with indices $d \in \Dcal'$, where $\Dcal'$ is given in~(\ref{eqn:kept-feature-set}).
%
\begin{align}
	\Fcal_i(j) &\coloneqq (\hat{\mu}_{ij} - k \hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij}) \cap (-c, +c),
	\label{eqn:fij} \\
	\Dcal' &\coloneqq \left\{ j \in [D] : \exists i \in [B] \textrm{ s.t. }  \Fcal_i(j) = \emptyset \right\}
	\label{eqn:kept-feature-set}
\end{align}
%
Intuitively, this means discarding any feature $j$ for which 
$(\hat{\mu}_{ij} - k\hat{\sigma}_{ij}, \hat{\mu}_{ij} + k \hat{\sigma}_{ij})$ overlaps with
$(-c, c)$ for all block indices $i$. If we were to use the Laplace approximation for the posterior $p(W_{ij} | A, X) \approx \Gaussian(W_{ij}; \hat{\mu}_{ij}, \hat{\sigma}_{ij}^2)$, then this is analogous to a hypothesis test on the value of $W_{ij}$ as in~(\ref{eqn:hyp-test-discard});
then $\Dcal'$ comprises all features $j$ for which $H_1$ is accepted at least once for some $i \in [B]$.
%
\begin{equation}
	H_0: |W_{ij}| \leq c \qquad
	H_1: |W_{ij}| > c
	\label{eqn:hyp-test-discard}
\end{equation}
%
The multiplier $k$ in~(\ref{eqn:fij}) determines the degree of significance of the result. However, as the Laplace approximation is not exact, we regard this as a useful heuristic and not an exact method. Conversely, we could fix $k=k_0$ and the dimension of our reduced feature set $|\Dcal'|=D'$. We would then like to find the largest value of $c$ such that $|\Dcal'|=D'$ given $k=k_0$:
%
\begin{equation}
	c^* = \argmax \{c>0\; : \;|\Dcal'| = D', k=k_0\}.
	\label{eqn:c-star}
\end{equation}
%
This has the advantage of fixing the number of reduced dimensions.
